FoRTE baseline

### 2019-04-23 analysis/paper/paper.Rmd
Add "bigfacet" code and plot

- Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure

```{r summary-captions}
summary_ts_cap <- paste(
  "ED2 plot-level predictions by model configuration."
)
```

@@

>>>>

Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure

```{r summary-captions}
summary_ts_cap <- paste(
  "ED2 plot-level predictions by model configuration."
)

bigfacet_cap <- paste(
  "ED2 PFT-level predictions of leaf area index (LAI) by model configuration and parameterization."
)
```

@@

`r mdcap(summary_ts_cap)`

Big facet plot (exploratory) of LAI by PFT for all model combinations

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 12)}
readd(bigfacet_plot)
```
